Spray particle drift

### 2021-07-14 manuscript.Rmd
h

>>>>

## Experimental sites

Field experiments were conducted in three locations: North Platte, NE (geographic coordinates) on September 11-12/2021; Arlington, WI (geographic coordinates) on September 15-16/2021; and city, MO (geographic coordinates) on September 18-20/2021. In NE, WI, and MO, applications were made on bare ground, corn stubble (XX cm height) and ????, respectively. The fields were flat and with no surrounding trees. Samples were processed and analyzed at the Pesticide Application Technology Laboratory of the University of Nebraska-Lincoln located in North Platte, Nebraska.

## Field study

Three factors were evaluated: sprayer type, nozzle type, and spray solution. Each experimental treatment was replicated 10 times. Two sprayers (Manufacturer, city, state) were employed for this study, the only difference being the inclusion of a hood or no hood. These sprayers were 9.1 meters in width and each had a 1130 L polyethylene tank. Spray delivery was accomplished via a hydraulic pump driven by the accompanying tractor. Each sprayer was connected to its own tractor via the three-point hitch system. Nozzle spacing was 51 cm, and boom height was set at 90 cm above the ground level for both sprayers. The wind skirt on the hooded sprayer was set slightly above the soil surface or corn stubble. The height for each sprayer was maintained throughout the study via the sprayers’ guide wheels and the tractors’ hitch system. The hood was constructed of molded, polymer plastic that surrounded the nozzles (Manufacturer, city, state). The hood sections reached approximately 30.5 cm below the nozzle orifices, and a plastic curtain reached a further 10 cm below the plastic hood. Nozzles were properly attached to the boom in order to get no interference of hood and nozzle plume.

Nozzle types were TTI11003 and AIXR11003 (Teejet Technologies, Wheaton, IL), and ULD12003 (Pentair, Minneapolis, MN). All nozzles have air inclusion features and the carrier volume was 140 L ha^-1 applied at 276 kPa operating pressure and 2.6 m s-1 application speed.

The spray solutions were prepared at the same day of applications and were water alone and water plus a drift-reducing adjuvant based on polyethylene glycol, choline chloride, and guar gum (IntactTM, Precision Laboratories, LLC, Waukegan, IL) at a rate of 0.5% v v-1. Additionally, a rhodamine fluorescent dye (Red Dye, Cole-Parmer, Vernon Hills, IL) was added to all solutions at a rate of 0.5% v v-1. The volumetric median diameter (VMD) of droplets and volume percentage of droplets finer than 200 μm (V200) were measured at the Pesticide Application Technology Laboratory using a Sympatec Helos-Vario K/R laser diffraction system (Sympatec Inc., Clausthal, Germany), setup with a R7 lens, with a dynamic size range of 9 to 1,800 μm. The distance from the nozzle tip to the laser was 0.3 m. The VMD and V200 for each combination spray solution versus nozzle type are listed in Table 1.

## Application and field layout

Prior to the applications, 27 drift collection stations were placed downwind of the sprayed area in three transects (spaced by 7.6 m) and perpendicular to the spray line (Figure 1). For each transect, collectors were positioned at 1, 2, 3, 4, 8, 16, 31, 45, 60 m from the edge of the application zone. Additionally, three drift stations were placed 5 m upwind from the edge of the application zone and four petri dishes (150 mm diameter) were placed in-swath. All collectors were positioned 10 cm above the ground surface.
Mylar cards (Grafix Plastics, Cleveland, OH) were used as drift collectors. Cards with dimensions of 10 x 10 cm were placed upwind and up to 31 m downwind, whereas cards with dimensions of 20 x 20 cm were placed at 45 and 60 m downwind.

Each replication was considered as one pass of the sprayer, equivalent to 828 m2 in total area (91 m length x 9.1 m wide). Before each pass, a new set of mylar cards and petri dishes were placed at the sampling points. Five minutes after the end of each application was performed, cards and petri dishes were collected and placed individually into pre-labeled plastic bags. All samples were carefully managed to avoid cross-contamination and stored into dark containers until further analysis in laboratory in order to prevent photodegradation of rhodamine dye. Samples were collected from the furthest to the nearest downwind distance. Different teams were designated to work at downwind, upwind, and in-swath zones, and gloves were changed between application passes.

The targeted wind velocity was between 3.6 to 6.7 m s-1 and ± 30° of being perpendicular to the driveline before applying a treatment. When necessary, the driveline and application zone was shifted to maintain the ± 30° wind direction target. Meteorological conditions (air temperature, and relative humidity, wind speed, wind direction) were collected at 2 m height and 1-min intervals using a HOBO RX3000 Weather Station (Onset Computer Co., Bourne, MA, USA) positioned upwind of the sprayed area. The wind speed and direction data were collected using 2D WindSonic anemometers (Gill Instruments, Lymington, UK). The meteorological data for each respective treatment is listed in Figure 2.

## Dye quantification

Samples were taken to the laboratory for dye extraction and quantification using fluorometry technique. Distilled water was used as extraction solution added to each bag using a bottle top dispenser (LabSciences Inc., 60000-BTR, Reno, NV). Samples collected downwind were rinsed with 50 mL of distilled water, whereas samples collected upwind and in-swath were rinsed with 20 mL of distilled water. The samples were agitated for 15 s and then a 1.5 mL aliquot from each sample bag was drawn to fill a glass cuvette. The cuvette was placed in a rhodamine module inside a fluorometer (Trilogy 7200.000, Turner Designs, Sunnyvale, CA) using green light. Serial dilutions were performed upon each tank sample to generate calibration curves, which allowed the conversion of relative fluorescence unit into mg L-1 and further expressing data into ɳL cm-2.

### 2021-07-14 manuscript.tex
h

\title{Spray particle drift}
\author{Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo
Werle}
\date{2021-06-22}

@@

@@

The statistical analyses were conducted with R statistical software
version 4.1.0.\textsuperscript{1} Data analyses were performed with
Bayesian inference with ``brms'' package.\textsuperscript{2} Bayesian
inference uses Markov chain Monte Carlo algorithms for sampling a
probability distribution;\textsuperscript{2} and avoid singular fit from
frequentist linear models when using complex random effects.

@@

Data was fitted to a mixed model using \emph{brm} function. Treatments
were the fixed effects and block nested within location random effects.
Model family was gaussian and prior distribution was set to student-t
with mean 0.5, standard deviation 3 and 11 degrees of freedom. The
posterior summaries (mean and highest posterior density) were estimated
with \emph{emmeans} function from ``emmeans'' package. Treatment means
were compared using Bayes Factor (BF).\textsuperscript{3,4} In short, if
BF \textgreater{} 1 there is evidence for H1 (difference between
treatments); whereas, if H0 \textless{} 1 there is evidence for H0 (no
difference between treatments). If BF = 1, there is no evidence. The
level of evidence (anecdotal, moderate, strong, very strong, and
extreme) varies as the BF value increase (evidence for H1) or decrease
(evidence for H0).

@@

Data was fitted to a Bayesian linear mixed model using \emph{brm}
function. Spray solution deposition and distance were log-transformed to
meet linearity. A single model was fitted to each treatment. For each
model, treatments and distance were the fixed effects and block nested
within location random effects. Model family was gaussian and prior
distribution was set to student-t with mean 0.5, standard deviation 3
and 11 degrees of freedom. For clarification, intercepts, slopes were
back-transformed with \emph{exponential} function. Moreover, the linear
models fitted were used to predict the distance where no spray particle
deposition was detected (0 ηL cm\textsuperscript{-2}) for each
treatment, which was also back-transformed to m scale.

The area under the curve (AUC) was used to validate the linear models.
The spray solution deposition across distances within a experimental
unit were used to calculate the absolute AUC value. The AUC was
performed with \emph{audps} function from ``agricolae'' package. The AUC
is commonly used for plant disease progress\textsuperscript{5,6} but has
been used to calculate herbicide injury.\textsuperscript{7} Data was
fitted to a mixed model using \emph{brm} function. Treatments were the
fixed effects and block nested within location random effects. Model
family was gaussian and prior distribution was set to student-t with
mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior
summaries (mean and highest posterior density) were estimated with
\emph{emmeans} function from ``emmeans'' package. Treatment means were
compared using Bayes Factor (BF) as above-mentioned.

@@

In general, Open sprayer treatments resulted in a more variable spray
particle deposition than Hood treatments (Figure 1). The inclusion of
either DRA or Water strongly impacted spray particle deposition inswath
for Open sprayer treatments, regardless nozzle type. The top and bottom
three treatments contained either DRA or Water, respectively. For
example, treatment DRA-Open-ULD resulted in the highest spray particle
deposition (1318.5 ηL cm\textsuperscript{-2}, Figure 1). In contrast,
911.2 nL cm\textsuperscript{-2} was the lowest spray solution
deposition, which was achieved with Water-Open-ULD treatment. Hood
sprayer treatments resulted in a more uniform spray particle deposition.
Furthermore, there were less than 0.29 ηL cm\textsuperscript{-2} spray
deposition at upwind with a strong evidence (BF \textless{} 0.25) of no
difference between all pairwise treatments contrasts (data not shown).

@@

Similar trend was observed to AUC. Treatments with Hood or Open sprayer
strongly impacted on AUC values (Figure 3B). The highest AUC values were
Water-Open-AIXR (87.4), followed by Water-Open-ULD (72.9) and
DRA-Open-AIXR (72.6). In contrast, DRA-Hood-TTI (13.9), DRA-Hood-ULD
(14.3) and Water-Open-AIXR (21.9) resulted in lowest AUC values. The
impact of Open and Hood sprayer is demonstrated in treatments including
AIXR nozzle. There is a high difference in AUC (50.7) between
DRA-Open-AIXR vs DRA-Hood-AIXR (BF \textgreater{} 100). Moreover,
addition of DRA did reduced AUC values when comparing within fixed
factors, sprayer (Hood and Open) and nozzle (AIXR, TTI and ULD);
however, addition of DRA were not statistically different for some
contrasts, including DRA-Hood-TTI vs Water-Hood-TTI (BF = 0.91),
DRA-Open-TTI vs Water-Open-TTI (BF = 0.55), and DRA-Open-AIXR vs
Water-Open-AIXR (BF = 0.93).

>>>>

\title{Spray particle drift}
\author{Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo
Werle}
\date{2021-07-14}

@@

\hypertarget{experimental-sites}{%
\subsection{Experimental sites}\label{experimental-sites}}

Field experiments were conducted in three locations: North Platte, NE
(geographic coordinates) on September 11-12/2021; Arlington, WI
(geographic coordinates) on September 15-16/2021; and city, MO
(geographic coordinates) on September 18-20/2021. In NE, WI, and MO,
applications were made on bare ground, corn stubble (XX cm height) and
????, respectively. The fields were flat and with no surrounding trees.
Samples were processed and analyzed at the Pesticide Application
Technology Laboratory of the University of Nebraska-Lincoln located in
North Platte, Nebraska.

\hypertarget{field-study}{%
\subsection{Field study}\label{field-study}}

Three factors were evaluated: sprayer type, nozzle type, and spray
solution. Each experimental treatment was replicated 10 times. Two
sprayers (Manufacturer, city, state) were employed for this study, the
only difference being the inclusion of a hood or no hood. These sprayers
were 9.1 meters in width and each had a 1130 L polyethylene tank. Spray
delivery was accomplished via a hydraulic pump driven by the
accompanying tractor. Each sprayer was connected to its own tractor via
the three-point hitch system. Nozzle spacing was 51 cm, and boom height
was set at 90 cm above the ground level for both sprayers. The wind
skirt on the hooded sprayer was set slightly above the soil surface or
corn stubble. The height for each sprayer was maintained throughout the
study via the sprayers' guide wheels and the tractors' hitch system. The
hood was constructed of molded, polymer plastic that surrounded the
nozzles (Manufacturer, city, state). The hood sections reached
approximately 30.5 cm below the nozzle orifices, and a plastic curtain
reached a further 10 cm below the plastic hood. Nozzles were properly
attached to the boom in order to get no interference of hood and nozzle
plume.

Nozzle types were TTI11003 and AIXR11003 (Teejet Technologies, Wheaton,
IL), and ULD12003 (Pentair, Minneapolis, MN). All nozzles have air
inclusion features and the carrier volume was 140 L ha\^{}-1 applied at
276 kPa operating pressure and 2.6 m s-1 application speed.

The spray solutions were prepared at the same day of applications and
were water alone and water plus a drift-reducing adjuvant based on
polyethylene glycol, choline chloride, and guar gum (IntactTM, Precision
Laboratories, LLC, Waukegan, IL) at a rate of 0.5\% v v-1. Additionally,
a rhodamine fluorescent dye (Red Dye, Cole-Parmer, Vernon Hills, IL) was
added to all solutions at a rate of 0.5\% v v-1. The volumetric median
diameter (VMD) of droplets and volume percentage of droplets finer than
200 μm (V200) were measured at the Pesticide Application Technology
Laboratory using a Sympatec Helos-Vario K/R laser diffraction system
(Sympatec Inc., Clausthal, Germany), setup with a R7 lens, with a
dynamic size range of 9 to 1,800 μm. The distance from the nozzle tip to
the laser was 0.3 m. The VMD and V200 for each combination spray
solution versus nozzle type are listed in Table 1.

\hypertarget{application-and-field-layout}{%
\subsection{Application and field
layout}\label{application-and-field-layout}}

Prior to the applications, 27 drift collection stations were placed
downwind of the sprayed area in three transects (spaced by 7.6 m) and
perpendicular to the spray line (Figure 1). For each transect,
collectors were positioned at 1, 2, 3, 4, 8, 16, 31, 45, 60 m from the
edge of the application zone. Additionally, three drift stations were
placed 5 m upwind from the edge of the application zone and four petri
dishes (150 mm diameter) were placed in-swath. All collectors were
positioned 10 cm above the ground surface. Mylar cards (Grafix Plastics,
Cleveland, OH) were used as drift collectors. Cards with dimensions of
10 x 10 cm were placed upwind and up to 31 m downwind, whereas cards
with dimensions of 20 x 20 cm were placed at 45 and 60 m downwind.

Each replication was considered as one pass of the sprayer, equivalent
to 828 m2 in total area (91 m length x 9.1 m wide). Before each pass, a
new set of mylar cards and petri dishes were placed at the sampling
points. Five minutes after the end of each application was performed,
cards and petri dishes were collected and placed individually into
pre-labeled plastic bags. All samples were carefully managed to avoid
cross-contamination and stored into dark containers until further
analysis in laboratory in order to prevent photodegradation of rhodamine
dye. Samples were collected from the furthest to the nearest downwind
distance. Different teams were designated to work at downwind, upwind,
and in-swath zones, and gloves were changed between application passes.

The targeted wind velocity was between 3.6 to 6.7 m s-1 and ± 30° of
being perpendicular to the driveline before applying a treatment. When
necessary, the driveline and application zone was shifted to maintain
the ± 30° wind direction target. Meteorological conditions (air
temperature, and relative humidity, wind speed, wind direction) were
collected at 2 m height and 1-min intervals using a HOBO RX3000 Weather
Station (Onset Computer Co., Bourne, MA, USA) positioned upwind of the
sprayed area. The wind speed and direction data were collected using 2D
WindSonic anemometers (Gill Instruments, Lymington, UK). The
meteorological data for each respective treatment is listed in Figure 2.

\hypertarget{dye-quantification}{%
\subsection{Dye quantification}\label{dye-quantification}}

Samples were taken to the laboratory for dye extraction and
quantification using fluorometry technique. Distilled water was used as
extraction solution added to each bag using a bottle top dispenser
(LabSciences Inc., 60000-BTR, Reno, NV). Samples collected downwind were
rinsed with 50 mL of distilled water, whereas samples collected upwind
and in-swath were rinsed with 20 mL of distilled water. The samples were
agitated for 15 s and then a 1.5 mL aliquot from each sample bag was
drawn to fill a glass cuvette. The cuvette was placed in a rhodamine
module inside a fluorometer (Trilogy 7200.000, Turner Designs,
Sunnyvale, CA) using green light. Serial dilutions were performed upon
each tank sample to generate calibration curves, which allowed the
conversion of relative fluorescence unit into mg L-1 and further
expressing data into ɳL cm-2.

@@

The statistical analyses were conducted with R statistical software
version 4.1.0.\textsuperscript{1} Data analyses were performed with
Bayesian inference with ``brms'' package.\textsuperscript{2} Bayesian
inference uses Markov chain Monte Carlo algorithms for sampling a
probability distribution;\textsuperscript{2} and avoids singular fit
from frequentist linear models when using complex random effects.

@@

Data was fitted to a mixed model using \emph{brm} function. Treatments
were the fixed effects and blocks nested within location random effects.
Model family was gaussian and prior distribution was set to student-t
with mean 0.5, standard deviation 3 and 11 degrees of freedom. The
posterior summaries (mean and highest posterior density) were estimated
with \emph{emmeans} function from the ``emmeans'' package. Treatment
means were compared using Bayes Factor (BF).\textsuperscript{3,4} In
short, if BF \textgreater{} 1 there is evidence for H1 (difference
between treatments); whereas, if H0 \textless{} 1 there is evidence for
H0 (no difference between treatments). If BF = 1, there is no evidence.
The level of evidence (anecdotal, moderate, strong, very strong, and
extreme) varies as the BF value increases (evidence for H1) or decreases
(evidence for H0).

@@

Data was fitted to a Bayesian linear mixed model using \emph{brm}
function. Spray solution deposition and distance were log-transformed to
meet linearity. A single model was fitted to each treatment. For each
model, treatments and distance were the fixed effects and blocks nested
within location random effects. Model family was gaussian and prior
distribution was set to student-t with mean 0.5, standard deviation 3
and 11 degrees of freedom. For clarification, intercepts, slopes were
back-transformed with \emph{exponential} function. Moreover, the linear
models fitted were used to predict the distance where no spray particle
deposition was detected (0 ηL cm\textsuperscript{-2}) for each
treatment, which was also back-transformed to m scale.

The area under the curve (AUC) was used to validate the linear models.
The spray solution deposition across distances within an experimental
unit were used to calculate the absolute AUC value. The AUC was
performed with \emph{audps} function from the ``agricolae'' package. The
AUC is commonly used for plant disease progress\textsuperscript{5,6} but
has been used to calculate herbicide injury.\textsuperscript{7} Data was
fitted to a mixed model using \emph{brm} function. Treatments were the
fixed effects and blocks nested within location random effects. Model
family was gaussian and prior distribution was set to student-t with
mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior
summaries (mean and highest posterior density) were estimated with
\emph{emmeans} function from the ``emmeans'' package. Treatment means
were compared using Bayes Factor (BF) as above-mentioned.

@@

In general, Open sprayer treatments resulted in a more variable spray
particle deposition than Hood treatments (Figure 1). The inclusion of
either DRA or Water strongly impacted spray particle deposition inswath
for Open sprayer treatments, regardless nozzle type. The top and bottom
three treatments contained either DRA or Water, respectively. For
example, treatment DRA-Open-ULD resulted in the highest spray particle
deposition (1318.5 ηL cm\textsuperscript{-2}, Figure 1). In contrast,
911.2 nL cm\textsuperscript{-2} was the lowest spray solution
deposition, which was achieved with Water-Open-ULD treatment. Hood
sprayer treatments resulted in a more uniform spray particle deposition.
Furthermore, there were less than 0.29 ηL cm\textsuperscript{-2} spray
deposition at upwind with strong evidence (BF \textless{} 0.25) of no
difference between all pairwise treatment contrasts (data not shown).

@@

Similar trend was observed in AUC. Treatments with Hood or Open sprayer
strongly impacted on AUC values (Figure 3B). The highest AUC values were
Water-Open-AIXR (87.4), followed by Water-Open-ULD (72.9) and
DRA-Open-AIXR (72.6). In contrast, DRA-Hood-TTI (13.9), DRA-Hood-ULD
(14.3) and Water-Open-AIXR (21.9) resulted in lowest AUC values. The
impact of Open and Hood sprayer is demonstrated in treatments including
AIXR nozzles. There is a high difference in AUC (50.7) between
DRA-Open-AIXR vs DRA-Hood-AIXR (BF \textgreater{} 100). Moreover,
addition of DRA did reduced AUC values when comparing within fixed
factors, sprayer (Hood and Open) and nozzle (AIXR, TTI and ULD);
however, addition of DRA were not statistically different for some
contrasts, including DRA-Hood-TTI vs Water-Hood-TTI (BF = 0.91),
DRA-Open-TTI vs Water-Open-TTI (BF = 0.55), and DRA-Open-AIXR vs
Water-Open-AIXR (BF = 0.93).
